Calendar-based graphics for visualising people's daily schedules

### 2017-07-10 main.Rmd
Added day of month text to boxplot

```{r boxplot, fig.height = 6.5, fig.cap = "Boxplot of hourly counts across all the 43 sensors in December of 2016, with the superimposing hourly averages. It shows the hourly distribution in the city as a whole. Christmas stands out as the quietest day in December."}
```

>>>>

```{r boxplot, fig.height = 6.5, fig.cap = "Side-by-side boxplot of hourly counts across all the 43 sensors in December of 2016, with the superimposing hourly averages. It shows the hourly distribution in the city as a whole. Christmas stands out as the quietest day in December."}
```

### 2017-07-10 main.tex
Added day of month text to boxplot

\section{Other variations}\label{other-variations}

@@

\subsection{Lag scatterplot}\label{lag-scatterplot}

@@

\subsection{Boxplot}\label{boxplot}

@@

\caption[Boxplot of hourly counts across all the 43 sensors in December of 2016, with the superimposing hourly averages]{Boxplot of hourly counts across all the 43 sensors in December of 2016, with the superimposing hourly averages. It shows the hourly distribution in the city as a whole. Christmas stands out as the quietest day in December.}\label{fig:boxplot}
\end{figure}
\end{CodeChunk}

>>>>

\section{Variations}\label{variations}

@@

@@

\subsection{Different types of plots}\label{different-types-of-plots}

@@

\caption[Side-by-side boxplot of hourly counts across all the 43 sensors in December of 2016, with the superimposing hourly averages]{Side-by-side boxplot of hourly counts across all the 43 sensors in December of 2016, with the superimposing hourly averages. It shows the hourly distribution in the city as a whole. Christmas stands out as the quietest day in December.}\label{fig:boxplot}
\end{figure}
\end{CodeChunk}
